Naming Anonymous JavaScript Functions

### 2011-04-14 papers/splash-wavefront2011/sigplanconf-template.tex
complete appendix 1

%\appendix
%\section{JavaScript Projects Analyzed for Function Names}
%\begin{description}
%\item[Closure] Google Web Library, ...
%\item[Dojo] JavaScript Toolkit
%\item[ExtJS] JavaScript Framework
%\item[Firebug] Web Page Debugger, http://code.google.com/p/fbug/, version 1.7??
%\item[jQuery]
%\item[MochiKit]
%\item[MooTools]
%\item[Prototype]
%\item[Scriptaculous]
%\item[YUI]
%\end{description}

>>>>

\appendix
\section{JavaScript Projects Analyzed for Function Names}
\begin{description}
\item[Closure] Closure Library, r683, Google Code, \\
http://code.google.com/p/closure-library/
\item[Dojo] Dojo JavaScript Toolkit, version 1.5, \\
http://dojotoolkit.org/
\item[ExtJS] JavaScript Framework, version 3.3.1 \\
http://www.sencha.com/products/extjs/
\item[Firebug] Web Page Debugger, version 1.7 \\
 http://code.google.com/p/fbug/.
\item[jQuery] JavaScript Library, version 1.4.4\\
http://jquery.com/
\item[MochiKit] version 1.4.2 \\
http://mochi.github.com/mochikit/
\item[MooTools] JavaScript Framework, version 1.3 \\
http://mootools.net/
\item[Prototype] JavaScript Framework, version 1.7 \\
http://www.prototypejs.org/
\item[Scriptaculous] JavaScript Library, version 1.9 \\
http://script.aculo.us/
\item[YUI] Library, Yahoo, Inc., version 3.3 \\
http://developer.yahoo.com/yui/
\end{description}
